Scheduling and Amortization for MPC

### 2022-02-19 biometric_vectorization_example.tex
Phases 3-4 of Basic Vectorization.

@@

sum!2 = [0,..,0]
sum!2^ = raise_dim(sum!2, (j:D!0))
d!3[I,J] = SUB_SIMD(S!0^[I,J],C!0^[I,J])
p!3[I,J] = MUL_SIMD(d!3[I,J] * d!3[I,J])

for j in range(0, D!0):
  sum!3[I,j] = PHI(sum!2^[I,j], sum!4[I,j-1])       
  sum!4[I,j] = ADD_SIMD(sum!3[I,j],p!3[I,j])

sum!3^ = drop_dim(sum!3)     
min_index!3 = [0,1,...N!0-1]   
min_sum!3 = sum!3^

for i in range(0, N!0):
  min_sum!2[i] = PHI(min_sum!1^[i], min_sum!4[i-1]) 
  !1!2[i] = CMP(sum!3^[i],min_sum!2[i])
  min_sum!4[i] = MUX(!1!2[i], min_sum!3[i], min_sum!2[i])

And this phase gets rid of redundant dimensionality. Code moves back to 
a version close to the original one.

>>>>

This phase removes redundant dimensionality. 
It starts by removing redundant dimensions in MOTION loops followed
by removal of redundant drop dimension statements.
It then does (extended) constant propagation 
to "bypass" raise statements, copy propagation
and dead code elimination.

The code becomes closer to what we started with:

sum!2 = [0,..,0]
d!3[I,J] = S!0^[I,J] - C!0^[I,J]
p!3[I,J] = (d!3[I,J] * d!3[I,J])

// j is redundant for sum!3 and sum!4
for j in range(0, D!0):
  sum!3[I] = PHI(sum!2^[I], sum!4[I])       
  sum!4[I] = (sum!3[I] + p!3[I,j])

// drop_dim is redundant, removing
// then copy propagation and dead code elimination 
min_index!3 = [0,1,2,...N!0-1] // or min_index!3 = [i, (i:N!0)]

// i is redundant for min_sum!2, min_sum!4 but not for !12![i]!
for i in range(0, N!0):
  min_sum!2 = PHI(min_sum!1, min_sum!4) 
  !1!2[i] = (sum!3[i] < min_sum!2)
  min_sum!4 = MUX(!1!2[i], sum!3[i], min_sum!2)

// same, i is redundant for min_index!2, min_index!4
for i in range(0, N!0):
  min_index!2 = PHI(min_index!1, min_index!4)  
   min_index!4 = MUX(!1!2[i], min_index!3[i], min_index!2)

// drop_dim becomes redundant
!2!1 = (min_sum!2, min_index!2)
\end{verbatim}
}

@@

### 2022-02-19 paper_SIMD.tex
Edits on Phase 4.
Phases 3-4 of Basic Vectorization.

\COMMENT {{\color{red} $cl_1$ and $cl_2$ intersect if they have common statement, or update same array; "intersect" definition can be expanded}}

\WHILE {there are closure $cl_1$ and $cl_2$ that intersect}
\STATE {merge $cl_1$ and $cl_2$}
\ENDWHILE
\FOR {each closure $cl$ (after merge)}
\STATE {create FOR $i_d = 0; ...$ loop}
\STATE {add $\phi$-nodes in $cl$ to header block}
\STATE {{\color{red}{add target-less $\phi$-node for A if $cl$ updates array A}}}
\STATE {add statements in $cl$ to loop body in some order of dependences}
\STATE \COMMENT {Dimension is not vectorizable: }
\STATE {change $\stackrel{\rightarrow}{i_d}$ to $i_d$ in all statements in loop}
\STATE {treat FOR loop as monolith node: change def-use edges accordingly. Some edges become same-level.}
\ENDFOR
{
\color{red}
\FOR {each target-less $\phi$-node $A_1 = \phi(A_0,A_k)$}
\STATE {in vectorizable stmts, replace use of $A_1$ with $A_0$}
\STATE {discard $\phi$-node if not used in any $cl$}
\ENDFOR
}
\ENDFOR

\COMMENT {Phase 3:}
\STATE {add SIMD for simdified dimensions}

>>>>

\COMMENT {{\color{red} $cl_1$ and $cl_2$ intersect if they have common statement or update same array; "intersect" definition can be expanded}}

\WHILE {there are closure $cl_1$ and $cl_2$ that intersect}
\STATE {merge $cl_1$ and $cl_2$}
\ENDWHILE
\FOR {each closure $cl$ (after merge)}
\STATE {create FOR $i_d = 0; ...$ loop}
\STATE {add $\phi$-nodes in $cl$ to header block}
\STATE {{\color{red}{add target-less $\phi$-node for A if $cl$ updates array A}}}
\STATE {add statements in $cl$ to loop body in some order of dependences}
\STATE \COMMENT {Dimension is not vectorizable: }
\STATE {change $\stackrel{\rightarrow}{i_d}$ to $i_d$ in all statements in loop}
\STATE {treat FOR loop as monolith node: some def-use edges become same-level.}
\ENDFOR
{
\color{red}
\FOR {each target-less $\phi$-node $A_1 = \phi(A_0,A_k)$}
\STATE {in vectorizable stmts, replace use of $A_1$ with $A_0$}
\STATE {discard $\phi$-node if not used in any $cl$}
\ENDFOR
}
\ENDFOR

\COMMENT {Phase 3: Dimensionality reduction: remove unnecessary dimensionality. \ana{Better draft! Needs a bit more work.}}

\COMMENT { A dimension $i$ is dead on exit from stmt $X[...i...] = ...$ if all def-uses with targets outside of the enclosing 
FOR $i=0 ...$ MOTION loop end at target (use) $X' = \mathit{drop\_dim}(X, i)$. } 
\FOR {each stmt and dimension $X[...i...] = ...$}
\STATE {if $i$ is a dead dimension on exit from stmt $X[...i...] = ...$, remove $i$ from $X$} 
%\COMMENT{ A stmt v[...i] is a "dead dimension i" if all edges out of FOR i = 0; ... loop end at drop\_dim(v, i)}
\ENDFOR

\COMMENT {Now clean up drop\_dim and raise\_dim}
\FOR {each $X' =  \mathit{drop\_dim(X,i)}$ }
\STATE {replace with $X' = X$ if $i$ is dead in $X$.}
\ENDFOR
\STATE {do (1) (extended) constant propagation, (2) copy propagation and (3) dead code elimination to get rid of redundant variables and raise and drop dimension statements}

\COMMENT {Phase 4:}
\STATE {add SIMD for simdified dimensions}
